Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-06 article.tex
typo + abbreviation for auprc

% Metrics : ROC AUC an AUPRC
The network inference task can be viewed as a binary classification task
where one have to correctly classified the presence or the absence of edges
in the connectivity graph. Given the ground true network
$y_{i,j} \in \left\{0, 1\right\}$, the connectivity score matrix
$\hat{y}_{i,j} \in \mathcal{R}$ inferred by a given modeling technique
can be thresholded by a value $\tau \in \mathcal{R}$ to evaluate its performance. In this
context, we first define the notion of
true positive $tp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} \geq \tau)$,
true negative $tn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} < \tau)$,
false negative $fn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} < \tau)$ and
false positive $fp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} \geq \tau)$,
which is also called the confusion matrix.

We assess the accuracy of the network inference using the area under
the ROC curve (ROC AUC) obtained by varying the threshold
$\tau$ of the true positive rate $tpr(\tau) = tp(\tau) / (tp(\tau) + fn(\tau))$
as a function of the false positive rate
$fpr(\tau) = tn(\tau) / (tn(\tau) + fp(\tau))$. In section (TODO ref),
we also compare the same methods with the area under the precision-recall
curve obtained by varying the threshold
$\tau$ of the precision $P(\tau) = tp(\tau) / (tp(\tau) + fp(\tau))$
as a function of the recall $R(\tau) = tp(\tau) / (tp(\tau) + fn(\tau))$,
which is an information retrieval measure.

>>>>

% Metrics : ROC AUC and AUPRC
The network inference task can be viewed as a binary classification task
where one have to correctly classified the presence or the absence of edges
in the connectivity graph. Given the ground true network
$y_{i,j} \in \left\{0, 1\right\}$, the connectivity score matrix
$\hat{y}_{i,j} \in \mathcal{R}$ inferred by a given modeling technique
can be thresholded by a value $\tau \in \mathcal{R}$ to evaluate its performance. In this
context, we first define the notion of
true positive $tp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} \geq \tau)$,
true negative $tn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} < \tau)$,
false negative $fn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} < \tau)$ and
false positive $fp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} \geq \tau)$,
which is also called the confusion matrix.

We assess the accuracy of the network inference using the area under
the ROC curve (ROC AUC) obtained by varying the threshold
$\tau$ of the true positive rate $tpr(\tau) = tp(\tau) / (tp(\tau) + fn(\tau))$
as a function of the false positive rate
$fpr(\tau) = tn(\tau) / (tn(\tau) + fp(\tau))$. In section (TODO ref),
we also compare the same methods with the area under the precision-recall
(AUPRC) curve obtained by varying the threshold
$\tau$ of the precision $P(\tau) = tp(\tau) / (tp(\tau) + fp(\tau))$
as a function of the recall $R(\tau) = tp(\tau) / (tp(\tau) + fn(\tau))$,
which is an information retrieval measure.
